---
title: "Marc Presentación"
subtitle: "Data Analyst Day..."
author: "Marc25"
params:
  data: data
  data_train: data_train
  g1: g1
  g2: g2
institute: "cestudios.alonso"
date: "2021/05/02 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

???

Image credit: [Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Sharingan_triple.svg)

---
class: center, middle

# xa

### /Vamos a empezar..../

---
class: inverse, center, middle

# Get Started

---

# Good Morning Data 
I have a problem in my bussiness ...

--


--

# Example 01 : Loans predict default (Yes o No)
---

# Data Source 

```{r eval=require('flextable'), echo=FALSE}
str(params$data)
flextable(params$data[,1:7])
```

---

# R Plots Data Explorer

```{r eval=require('ggplot2'), fig.height=4, echo=TRUE}
library(ggplot2)
data <- as.data.frame(params$data)
g1 <- ggplot(data, aes(loan_default, ..count.., fill=loan_default))+
  geom_bar()+
  labs(title = "Target proportion in Data")
print.g1
```

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r}
knitr::kable(head(iris), format = 'html')
```

---

# HTML Widgets


---


---

```{r eval=require('DT'), tidy=FALSE}
DT::datatable(
  head(iris, 10),
  fillContainer = FALSE, options = list(pageLength = 8)
)
```

---
Apartado1 vs 2

.pull-left[

## Column 1

- First Bullet
```{r eval=require('flextable'), echo=FALSE}
flextable(as.data.frame(iris))
```
]

.pull-right[

## Column 2

- First Comparison
```{r eval=require('DT'), tidy=FALSE}
DT::datatable(
  head(iris, 10),
  fillContainer = FALSE, options = list(pageLength = 8)
)
```
]

   